### 2024-08-06 doc/Thesis/chapter/050-results-material.tex
finish editing 050 results material

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Material Properties of the Produced Layers}
\label{sec:res-mat}
%\todo{of what?}
%\subsection{Solution}
%%%%%%%% AQUATIC 
As already indicated in the experimental section the aqueous recipe adopted from Anwar et al.~\cite{Anwar2017} failed to produce a homogeneous layer of \gls{zro}.
The solution was opaque from the beginning and the resulting layers were patchy and laced with cracks (see figure~\ref{fig:sem-old}). 
Altering the ratio of ingredients, adjusting pH (by adding \gls{naoh}, \gls{h2so4} or \gls{hcl}) or adding \gls{sds} as surfactant did not increase the resistance of the resulting \gls{zro} layers. 
% ../../Data/SEM/SEM_2020_11_10_Old_Recipes/10_2L_19.tif
% ../../Data/SEM/SEM_2020_11_19_Old_Recipes/71_SL_NT4_11.tif
Even after the consecutive application of two layers, 
there was no significant improvement and the results examined with \gls{sem} (see figure~\ref{fig:sem-old}) reminded rather of a sparse crust than of a film. 
%It is assumed that the solution was far from the optimum for a sol-gel process. 
%
Figure~\ref{fig:sem-old} shows a typical detail view of \gls{zro} (dark) on top of \gls{fto} (finely polycrystalline). 
%These were the results of a single (figure~\ref{fig:sem-old1}) and double (figure~\ref{fig:sem-old2}) "layer" of the aqueous recipe. 
Large cracks, non-coated areas and inhomogeneity were 
%part of (ausmachen) 
shared characteristics among 
all samples created with the aqueous recipe. 
%even after several/multiple/various alteration to the recipe.

\begin{figure}[bht]
    \centering
    \begin{subfigure}{.45\textwidth}
        \centering
        %\includegraphics[width=.79\textwidth]{Pics/sem/071_fto_old_1x1F.png}
        \includegraphics[width=.99\textwidth]{Pics/sem/071_fto_old_2x.png}
		\caption{}%SEM picture of \gls{zro} produces by H2O solution} 
		\label{fig:sem-old}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/sem/147_steel_ph_10x.png}
		\caption{}%SEM picture of \gls{zro} produced by buoh solution} 
		\label{fig:sem-ph}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/sem/115_fto_cs_1x.png}
		\caption{}%115 fto cs 5x} 
		\label{fig:sem-cs1}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        %\includegraphics[width=.8\textwidth]{Pics/sem/147_steel_ph_10x.png}
        \includegraphics[width=.99\textwidth]{Pics/sem/150_steel_cs_2Fx5.png}
		\caption{}%150 steel 2Fx5} 
		\label{fig:sem-cs2}
    \end{subfigure}
	\caption{
		SEM images of of \gls{zro}:
		(a) \gls{zro} produces by 2 layers aqueous solution on \gls{fto}
		(b) 10 layers of \gls{zro} on steel substrate
		(c) cross section of crack of 5 layers of \gls{zro} on \gls{fto}
		(d) side view of scratched \gls{zro} on steel substrate
		%SEM images of \gls{zro} on top of \gls{fto} (a,c) and \gls{zro} on steel (b,d) \td{find bu sol on fto and show only steel}} 
		\label{fig:sem}
	}
\end{figure}
\enlargethispage{-\baselineskip}

The sol-gel recipe optimized by Hu et al.\cite{Hu2016} for \ch{Al2O3} worked splendidly for our use case even after (not so) minor changes (see section~\ref{sec:exp-sol-bu}). 
%
Figure~\ref{fig:sem-ph} shows a top view of 10 layers of the buthanolic solution on top of a steel substrate. 
%%%% PIN HOLES
The large irregularity on the bottom left could depict a pin hole, a (tiny) hole in the layer that reaches to the substrate. 
These irregularities are rather the exception. 
Alternatively, the small, hardly visible slits spread across the surface could depict such pin holes. 
% These - I think - are rather only one layer deep irregularities since they are so prevalent and hardly any pin holes were electrically observed on similar samples. \todo{where is the evidence?}

%%%%%% STABILITY
As soon as the solution showed initial cloudiness, it was declared as unstable and used no more for \gls{db}. %\td{(coating! DB = deutsche Bahn ... ist mir schon vorher aufgefallen)}
The visually asserted stability of the solution could be increased a lot by replacing the stabilizing agent \gls{acoh} with \gls{ipo}.
A \gls{1f} and a \gls{4f} solution with \gls{acoh} - sealed with Parafilm - was stable for approximately \h{24} and \h{2}, respectively.
%192 was first with IPOH
Whereas a \gls{4f} solution with \gls{ipo} as stabilizing agent stayed stable for circa \h{96}. 
An increase of the \gls{zrpro} concentration accelerates the aging process of the solution.
%\td{what is this aging process chemically? oxidation, hydrolization?}.
The aging process was accelerated by being in contact with "fresh" air in contrast to being sealed. 
It therefore dependent on the water in the air corresponding to an hyrolization process\cite{Hu2016}.
%
Only the introduction of \gls{ipo} into the recipe allowed higher concentrated solutions to be practicable 
as they could be stored until the next time needed, instead of producing a separate solution for each sample.
%
It was discovered that after a \gls{4f} \gls{acoh} solution has aged beyond cloudiness the addition 50\% of the volume in \gls{ipo} can even reverse the aging effect for a respectable amount of time. 
This effect is not only due to dilution as additional solvent (\gls{buoh}) did not re-stabilize the solution, 
even after 5 fold dilution. 
%Whereas addition of the original stabilizing agent \gls{buoh} to an aged solution had no effect. 
%Whereas, when the addition of the original stabilizing agent \gls{buoh} to an aged solution had no effect.

%%%%%%%%% CROSS SECTION
Figure~\ref{fig:sem-cs1} shows the cross-section of a layer of \gls{zro} on \gls{fto} glass at a deliberate fracture.
The large crystalline structure, which makes up most of the upper part of the image is \gls{fto}. 
The boundary to glass is visible at the very top. 
%On the lower edge of \gls{fto} a circa 100nm thick homogeneous layer can be observed: \gls{zro} produced by buthanolic recipe inspired by Hu et al..
On the lower edge of \gls{fto} a circa \nm{100} thick homogeneous layer of \gls{zro} (produced with 5 layers of \gls{1f} buthanolic \gls{acoh} recipe)  can be observed.
Measuring the cross section on steel was not as straight forward because the ductility of steel prevents fractures of the substrate. 
Resorting to scratching the surface with a diamond glass-cutter allowed us to get an insight into the thickness of the layer on steel substrate.
%
The result can be seen in figure~\ref{fig:sem-cs2}. 
5 layers of double concentrated solution were applied to this sample. 
Assuming that the raised structure resembling a tentacle is \gls{zro}, 
the thickness of the layer can be estimated to be in the order of magnitude of \nm{100}.

@@

\Gls{xrd} was used in order to confirm that the produced layer is indeed \gls{zro}. 
Figure~\ref{fig:xrd} shows diffractograms of the substrate (steel) and 
the substrate with ten layers of double concentrated solution (\gls{emma} experiment number 6113, see Appendix~\ref{sec:app-emma}).
In addition, two idealized diffractograms from the Crystallography Open Database of cubic \gls{zro} (COD ID 1521753\cite{gkatz1971xray}) and of $\alpha$-Fe (COD ID 1100108) are depicted.
%
The four largest peaks of the cubic \gls{zro} reference diffractogram at $2\theta=$ \ang{30}, \ang{51}, \ang{60}, \ang{35} (highest to lowest intensity) can also be observed in the experimental diffractogram. %. clearly stand out against the noise from the experimental diffractogram.
They confirm that the produced substance is indeed \gls{zro}.
Raman spectra are needed to further clarify the phase, 
since cubic and tetragonal phases are difficult to distinguish from \gls{xrd} alone\cite{Purohit2006Combustion}.

@@

In figure~\ref{fig:ir-gt} \gls{uv}/\gls{vis}/\gls{nir} transmission spectra of \gls{zro} layers on glass slides can be seen. 
Each sample had different numbers of layers. 
The incident angle was \ang{0} for each sample.
%differnt numbers of layers of \gls{zro} on a glass slide with 0 degree incident angle. 
The more layers, the more of the light is absorbed (at 600-\nm{1100}) by the \gls{zro} layers. 
%The trend is not monotonic due to inhomogenities in the sample???b
The thicker the layer is, the more wavy the graph, which can be attributed to interference\cite{Dumin1967}.
This trend can also be observed in figure~\ref{fig:ir-gr}.
The weak interference patterns at low wavelengths indicate that the thickness of the film is in the order of magnitude of the wavelengths\cite{delimafilho2017film} -- agreeing with \gls{sem} measurements. 
%
Figure~\ref{fig:ir-gr} shows reflectance spectra of \gls{uv}/\gls{vis}/\gls{nir} at an incident angle of \ang{45}. 
%The shift of the wavy part of the spectra (comparing reflectance with transmittance) can be explained by the longer path of light through the \gls{zro} layer because of the incident angle. 
Thicker layers reflect more light between approximately \nm{800} and \nm{1000}. 
Again, this effect is most likely not observed across the whole spectrum because of interferences. 
%It is interesting to note the shoulder at around \nm{850} present in every spectrum.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Material Properties of the Produced Layers}
\label{sec:res-mat}
%\todo{of what?}
%\subsection{Solution}
%%%%%%%% AQUATIC AQUEOUS
As already indicated in the experimental section the aqueous recipe adopted from Anwar et al.~\cite{Anwar2017} failed to produce a homogeneous layer of \gls{zro}.
The aqueous solution started out as opaque slurry in contrast to the buthanolic recipe which became opaque only after degrading. 
%\td{Die wässrige Lösung hatte direkt nach erzeugung viskose und undurchsichtige Eigenschaften - im Gegensatz zu der anderen Lösung, welche erst nach Stunden von klar auf undurchsichtig umschwenkte.}
%The solution was opaque from the beginning and 
Furthermore, the resulting layers were patchy and laced with cracks (see figure~\ref{fig:sem-old}). 
Altering the ratio of ingredients, adjusting pH (by adding \gls{naoh}, \gls{h2so4} or \gls{hcl}) or adding \gls{sds} as surfactant did not increase the measured resistance through the resulting \gls{zro} layers. 
% ../../Data/SEM/SEM_2020_11_10_Old_Recipes/10_2L_19.tif
% ../../Data/SEM/SEM_2020_11_19_Old_Recipes/71_SL_NT4_11.tif
Even after the consecutive application of two layers, 
there was no significant improvement and the \gls{sem} images (see figure~\ref{fig:sem-old}) 
showed highly inhomogeneous deposition, with deposited  areas next to other areas where the conductive substrate (ITO or FTO) can be clearly seen  uncoated.
%reminded rather of a sparse crust than of a film. 
%It is assumed that the solution was far from the optimum for a sol-gel process. 
%
Figure~\ref{fig:sem-old} shows a typical detail view of \gls{zro} (dark) on top of \gls{fto} (finely polycrystalline). 
%These were the results of a single (figure~\ref{fig:sem-old1}) and double (figure~\ref{fig:sem-old2}) "layer" of the aqueous recipe. 
Large cracks, non-coated areas and inhomogeneity were 
%part of (ausmachen) 
shared characteristics among 
all samples created with the aqueous recipe. 
%even after several/multiple/various alteration to the recipe.

\begin{figure}[bht]
    \centering
    \begin{subfigure}{.45\textwidth}
        \centering
        %\includegraphics[width=.79\textwidth]{Pics/sem/071_fto_old_1x1F.png}
        \includegraphics[width=.99\textwidth]{Pics/sem/071_fto_old_2x.png}
		\caption{}%SEM picture of \gls{zro} produces by H2O solution} 
		\label{fig:sem-old}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/sem/147_steel_ph_10x.png}
		\caption{}%SEM picture of \gls{zro} produced by buoh solution} 
		\label{fig:sem-ph}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/sem/115_fto_cs_1x.png}
		\caption{}%115 fto cs 5x} 
		\label{fig:sem-cs1}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        %\includegraphics[width=.8\textwidth]{Pics/sem/147_steel_ph_10x.png}
        \includegraphics[width=.99\textwidth]{Pics/sem/150_steel_cs_2Fx5.png}
		\caption{}%150 steel 2Fx5} 
		\label{fig:sem-cs2}
    \end{subfigure}
	\caption{
		SEM images of \gls{zro}:
		(a) \gls{zro} produces by 2 layers aqueous solution on \gls{fto}
		(b) 10 layers of \gls{zro} on steel substrate
		(c) cross section of crack of 5 layers of \gls{zro} on \gls{fto}
		(d) side view of scratched \gls{zro} on steel substrate
		%SEM images of \gls{zro} on top of \gls{fto} (a,c) and \gls{zro} on steel (b,d) \td{find bu sol on fto and show only steel}} 
		\label{fig:sem}
	}
\end{figure}
\enlargethispage{-\baselineskip}

The sol-gel recipe reported by Hu et al.\cite{Hu2016} and further optimzed, led to improved results (see section~\ref{sec:exp-sol-bu}). 
%
Figure~\ref{fig:sem-ph} shows a top view of 10 layers of the buthanolic solution on top of a steel substrate. 
%%%% PIN HOLES
The large irregularity on the bottom left could depict a pin hole, a hole in the layer that reaches to the substrate. 
These irregularities are rather the exception. 
Alternatively, the small, hardly visible cracks spread across the surface could depict such pin holes. 
% These - I think - are rather only one layer deep irregularities since they are so prevalent and hardly any pin holes were electrically observed on similar samples. \todo{where is the evidence?}

%%%%%% STABILITY
As soon as the solution showed initial cloudiness, it was declared as unstable and used no more for \gls{db}. %\td{(coating! DB = deutsche Bahn ... ist mir schon vorher aufgefallen)}
The solution becoming opaque indicated build-up of precipitation and was not further used.
The visually asserted stability of the solution could be increased a lot by replacing the stabilizing agent \gls{acoh} with \gls{ipo}.
A \gls{1f} and a \gls{4f} solution with \gls{acoh} - sealed with Parafilm - was stable for approximately \h{24} and \h{2}, respectively.
%192 was first with IPOH
Whereas a \gls{4f} solution with \gls{ipo} as stabilizing agent stayed stable for circa \h{96}. 
An increase of the \gls{zrpro} concentration accelerates the aging process of the solution.
%\td{what is this aging process chemically? oxidation, hydrolization?}.
The aging process was accelerated by absence of proper sealing.
\td{The aging process dependends on the water in the air corresponding to an hyrolization process\cite{Hu2016}.}
%
The introduction of \gls{ipo} into the recipe allowed higher concentrated solutions to be practicable 
as they could be stored until the next day, instead of producing a new, separate solution for each day.
%
It was found that after a \gls{4f} \gls{acoh} solution has 
%aged beyond cloudiness 
shown precipitation (became opaque)
the addition 50\% of the volume in \gls{ipo} can even reverse the aging effect for a respectable amount of time. 
This effect is not only due to dilution as additional solvent (\gls{buoh}) did not re-stabilize the solution, 
even after 5 fold dilution. 
%Whereas addition of the original stabilizing agent \gls{buoh} to an aged solution had no effect. 
%Whereas, when the addition of the original stabilizing agent \gls{buoh} to an aged solution had no effect.

%%%%%%%%% CROSS SECTION
Figure~\ref{fig:sem-cs1} shows the cross-section of a layer of \gls{zro} on \gls{fto} glass at a deliberate fracture.
The large crystalline structure, which makes up most of the upper part of the image is \gls{fto}. 
The boundary to glass is visible at the very top. 
%On the lower edge of \gls{fto} a circa 100nm thick homogeneous layer can be observed: \gls{zro} produced by buthanolic recipe inspired by Hu et al..
On the lower edge of \gls{fto} a circa \nm{100} thick homogeneous layer of \gls{zro} (produced with 5 layers of \gls{1f} buthanolic \gls{acoh} recipe) can be observed.
Measuring the cross section on steel was not as straight forward. 
%because the ductility of steel prevents fractures of the substrate. 
%Resorting to 
Scratching the surface with a diamond glass-cutter allowed us to get an insight into the thickness of the layer on steel substrate.
%
The result can be seen in figure~\ref{fig:sem-cs2}. 
5 layers of double concentrated solution were applied to this sample. 
Assuming that the raised structure resembling a tentacle is \gls{zro}, 
the thickness of the layer can be estimated to be in the order of magnitude of \nm{100}.

@@

\Gls{xrd} was used in order to confirm that the produced layer is indeed \gls{zro}. 
Figure~\ref{fig:xrd} shows diffractograms of the substrate (steel) and 
the substrate with ten layers of double concentrated solution (\gls{emma} experiment number 6113, see Appendix~\ref{sec:app-emma}).
In addition, two idealized diffractograms from the Crystallography Open Database of cubic \gls{zro} (COD ID 1521753\cite{gkatz1971xray}) and of $\alpha$-Fe (COD ID 1100108) are depicted.
%
The four largest peaks of the cubic \gls{zro} reference diffractogram at $2\theta=$ \ang{30}, \ang{51}, \ang{60}, \ang{35} (highest to lowest intensity) can also be observed in the experimental diffractogram. %. clearly stand out against the noise from the experimental diffractogram.
They confirm that the coated material is indeed \gls{zro}.
Raman spectra are needed to further clarify the phase, 
since cubic and tetragonal phases are difficult to distinguish from \gls{xrd} alone\cite{Purohit2006Combustion}.

@@

In figure~\ref{fig:ir-gt} \gls{uv}/\gls{vis}/\gls{nir} transmittance spectra of \gls{zro} layers on glass slides can be seen. 
Each sample had different numbers of coated layers. 
The incident angle was \ang{0} for each sample.
%differnt numbers of layers of \gls{zro} on a glass slide with 0 degree incident angle. 
The more layers, the more of the light is absorbed (at 600-\nm{1100}) by the \gls{zro} layers. 
%The trend is not monotonic due to inhomogenities in the sample???b
The thicker the layer is, the more wavy the graph, which can be attributed to interference\cite{Dumin1967}.
This trend can also be observed in figure~\ref{fig:ir-gr}.
The weak interference patterns at low wavelengths indicate that the thickness of the film is in the order of magnitude of the wavelengths\cite{delimafilho2017film} -- agreeing with \gls{sem} measurements. 
%
Figure~\ref{fig:ir-gr} shows reflectance spectra of \gls{uv}/\gls{vis}/\gls{nir} at an incident angle of \ang{45}. 
%The shift of the wavy part of the spectra (comparing reflectance with transmittance) can be explained by the longer path of light through the \gls{zro} layer because of the incident angle. 
Thicker layers reflect more light between approximately \nm{800} and \nm{1000}. 
Again, this effect is most likely not observed across the whole spectrum because of interferences. 
%It is interesting to note the shoulder at around \nm{850} present in every spectrum.
